% Set document class and font size
\documentclass[letterpaper, 11pt]{article}
\usepackage[utf8]{inputenc}

% Package imports
\usepackage{setspace, longtable, graphicx, hyphenat, hyperref, fancyhdr, ifthen, everypage, enumitem, amsmath, setspace}

% --- Page layout settings ---

% Set page margins
\usepackage[left=1in, right=1in, bottom=0.7in, top=0.7in]{geometry}

% Set line spacing
\renewcommand{\baselinestretch}{1.15}

% --- Page formatting ---

% Set link colors
\usepackage[dvipsnames]{xcolor}
\hypersetup{colorlinks=true, linkcolor=RoyalBlue, urlcolor=RoyalBlue}

% Set font to Libertine, including math support
\usepackage{libertine}
\usepackage[libertine]{newtxmath}

% Remove page numbering
\pagenumbering{gobble}

% --- Document starts here ---

\begin{document}

% Name and date of last update to this document
\noindent{\Huge{Hasha Dar}
\hfill{\it\footnotesize Updated \today}}

% --- Contact information and other items ---

\vspace{0.5cm} 
\begin{center}
\begin{tabular}{lll}
% Line 1: Email, GitHub, office location
\textbf{Email}: hd@hashadar.com      &
\hspace{0.4in} \textbf{GitHub}: github.com/hashadar    &
\hspace{0.3in} 	\textbf{Address}: 17 Manor Road \\

% Line 2: Phone number, LinkedIn, citizenship
\textbf{Phone}: +44 7305 576221   & 
\hspace{0.4in} \textbf{LinkedIn}: linkedin.com/in/hdar/   & 
\hspace{0.3in} Chigwell, Essex, IG7 5PF 
\end{tabular}
\end{center}

% --- Start the two-column table storing the main content ---

% Set spacing between columns
\setlength{\tabcolsep}{8pt}

% Set the width of each column
\begin{longtable}{p{1.3in}p{4.8in}}

% --- Section: Research interests ---

%\nohyphens{\color{OliveGreen}{Research interests}}
%& Your favorite topic, another topic, another topic, another topic, another topic \\
%& \\

% --- Section: Education ---

\color{OliveGreen}{Education} 
& \textbf{University College London} \\ 
& MEng Mechanical Engineering \hfill September 2019 -- Present \\
& Key modules: Manufacturing \& Design, \\
& Control \& Instrumentation, Thermodynamics and Fluid Dynamics II, \\
& Engineering Materials, Mathematical Modelling \& Analysis II, \\
& Engineering Dynamics, Mechanical Engineering Practical Skills,\\ 
& German Level 5 Business and Current Affairs.\\
& \\

& \textbf{Bancroft's School} \hfill London, UK \\
& A-Levels \hfill September 2017 -- June 2019\\
& Maths A*. Further Maths A, Physics A, German B\\
& \\
& GCSEs \hfill September 2015 -- June 2017 \\
& 4A*, 4A, 2B\\
& \\

% --- Uncomment the next few lines if you want to include some courses ---
%& \textbf{Selected coursework}
%\begin{itemize}[noitemsep,leftmargin=*]
%\item \underline{Relevant subject 1}: Course 1, Course 2, Course 3, Course 4
%\item \underline{Relevant subject 2}: Course 1, Course 2, Course 3, Course 4
%\end{itemize} \\

% --- Section: Publications ---
%\nohyphens{\color{OliveGreen}{Publications}} 
%& \textbf{Title of your most recent research paper} \\
%& First author, second author, third author, fourth author. \\
%& \textit{Journal of something or the other, 2020.}\\
%& \\

%& \textbf{Title of your second most recent research paper} \\
%& First author, second author, third author, fourth author. \\
%& \textit{Journal of something or the other, 2020.}\\
%& \\

%& \textbf{Title of your third most recent research paper} \\
%& First author, second author, third author, fourth author. \\
%& \textit{Journal of something or the other, 2020.}\\
%& \\

% --- Section: Relevant experience ---

\nohyphens{\color{OliveGreen}{Relevant experience}} 
& \textbf{UCL Racing Club} \\
& Formula 1 in Schools Mock Challenge \hfill January 2021 -- Present \\
& \textbf{CAD}: used Autodesk Fusion 360 to design the scale race car. \\
& \textbf{MATLAB}: used MATLAB (and Excel) to develop simulation models for the vehicle. \\
& \\

& \textbf{UCL Drone team} \\
& UCL Team Nova Student Engineer \hfill February 2020 -- Present \\
& \textbf{CAD}: used Autodesk Fusion 360 to design the frame of a race drone. \\
& \textbf{Marketing}: used Autodesk Fusion 360 to create promotional material for LinkedIn and Instagram. \\
& \\

& \textbf{UCL Formula Student Racing team} \\
& Assistant to Fourth Year Students \hfill October 2019 -- Present \\
& \textbf{Management}: worked on the costing and Bill of Materials for the Formula Student race car. \\
& \textbf{Electrical Design}: helped design electrical circuits for components on the race car. \\
& \\

% --- Section: Engineering projects ---

{\color{OliveGreen}{Engineering projects}} 
& \textbf{IMechE Challenge - Squash ball line launcher} \hfill Spring 2020 \\
& \textbf{Communication}: as the team leader, I liaised with and effectively distributed tasks among my team, playing to the various strengths of my team and meeting deadlines. \\
& \textbf{Design}: used CATIA V5 to produce our first prototype line launcher. MATLAB was also used for simulation and modelling. \\
& \textbf{End-to-end project management}: communication was primarily achieved through Microsoft Teams, where project files were uploaded and worked on together, including a 30 page design portfolio. \\
& \\

% --- Section: Other experience ---

{\color{OliveGreen}{Other experience}} 
& {\textbf{UCL Mechanical Engineering Department}}\\
& Student Ambassador \hfill January 2020 -- Present \\
& Attend department outreach events in the capacity of a current student e.g. Offer Holder Events, departmental tours.\\
& Panellist for interviews for senior teaching position for the Control and Instrumentation module.\\
& Part of the student media team in the department, responsible for interviewing staff, researchers and alumni.\\
& As a Transition Mentor, I am responsible for ten first year students, offering advice and signposting mentees to relevant resources.\\
& \\

% --- Section: Talks and tutorials ---

%{\color{OliveGreen}{Talks and tutorials}} 
%& \textbf{Title of your most recent presentation} \hfill Month Year \\
%& Name of conference, workshop, seminar, venue, etc., or a description \\
%& \\

%& \textbf{Title of your second most recent presentation} \hfill Month Year \\
%& Name of conference, workshop, seminar, venue, etc., or a description \\
%& \\

% --- Section: Service and outreach ---

\color{OliveGreen}{Service and outreach}
& \textbf{UCL Project Impactive} \hfill January 2021 -- Present \\
& CAD Mentor for the Accessibility Challenge 2021. I supported young children in developing skills on Autodesk Fusion 360 over the course of a three day event. \\
& \\

& \textbf{UCL Engineering Society} \hfill September 2020 -- Present \\
& Events Executive. I am responsible for arranging speakers to come in and deliver engaging talks from a variety of engineering related industries e.g. Mercedes AMG HPP and ARM. \\
& \\

& \textbf{UCL Mechanical Engineering Society} \hfill November 2020 -- Present \\
& Marketing Executive. I create content for use on social media channels such as Instagram and promote the activities of our society to the 1000+ students in the department. \\
& \\

% --- Section: Professional society memberships ---
% --- Note: section title is spread over two lines ---

%{\color{OliveGreen}{Professional}} 
%& {\textbf{Name of professional society.}} \hfill Month Year -- Present \\
%{\color{OliveGreen}{memberships}} 
%& Some things you did or conferences you attended. Aliquam volutpat est vel massa. Sed dolor lacus, imperdiet non, ornare non, commodo eu, neque. \\
%& \\

% --- Section: Various skills (programming, software, languages, etc.) ---

{\color{OliveGreen}{Skills}} 
& \textbf{Programming and software}\\
& Proficient in: Fusion 360, CATIA V5, MATLAB, \LaTeX, Office \& Adobe Suites. \\
& Familiar with: Simulink, ANSYS, C++, HTML, CSS, Python. \\
& \\

& \textbf{Languages} \\
& English (native), Urdu (mother tongue), German (advanced) \\
& \\

% --- Section: Awards, scholarships, etc. ---
% --- Note: section title is spread over two lines ---

{\color{OliveGreen}{Honours and}} 
& Arkwright Engineering Scholarship \hfill 2017\\
{\color{OliveGreen}{scholarships}} 
& \\
& \\

% --- Section: Other interests/hobbies ---

\nohyphens{\color{OliveGreen}{Other interests}} 
& President UCL Photo Society 20-21'. Co-Founder UCL Food Society 21'.\\ 
& Theatre Sound Designer for UCL productions (UCL Stage Crew)\\

% --- End of CV! ---

\end{longtable}
\end{document}