\section{Introduction}
\subsection{Team}
\begin{itemize}
	\item Mehran Moazen
	\item m.moazen@ucl.ac.uk
	\item Office hours: Tuesdays 9:00 - 11:00 Room 502 Roberts
\end{itemize}
\subsection{Assessment}
FEA coursework:
\begin{itemize}
	\item Coursework
	\item Software: ANSYS \& MATLAB
	\item Breakdown: no. 1a weighting 20\%, no. 1b weighting 30\%
	\item Deadline: 14th Nov
\end{itemize}
CFD coursework:
\begin{itemize}
	\item Coursework
	\item Software: CFD ACE \& CFD GEOM
	\item Breakdown: no. 1a weighting 20\%, no. 1b weighting 30\%
	\item Deadline: 23rd Jan
\end{itemize}
\section{FEA L1}
\subsection{Aims}
\begin{itemize}
	\item Understand the fundamentals concepts of the Finete Element Method
	\item Appreciate the structure of FE programs for potential amendment and development
	\item Expose asapects of the application of the method to engineering problems using a commerical software package (ANSYS)
	\item Taking a detached view in checking output and understand the limitations of the method
\end{itemize}
\subsection{Textbooks}
\begin{itemize}
	\item Fagan, M.J. (1992) Finete Element Analysis - Theory and Practice. Lecture material stemming from this textbook
	\item Seshu, P. (2012) Textbook of Finite Element Analysis. Chapter to be read from this book
\end{itemize}
\section{CFD L1}
\subsection{Aims}
\begin{itemize}
	\item Understanding the theoretical background
	\item Appreciating workflows and scheduling of pre-processing, simulation, post-processing and analysis
	\item Running commercial software packages nad assessing their limitations
	\item Using post-processing to analyse and present the results
	\item Taking a detached view in cehcking output
	\item Appreciating the structure of codes for potential amendment and development
\end{itemize}
Specific Aims
\begin{itemize}
	\item Theoretical basis of CFD, including governing equations for inviscid and viscous flows and equations for modelling turbulence
	\item CFD numerical methods covering discretisation schemes, including sources/sinks, with main focus on the Finite Volume approach. Numerical schemes for steady and unsteady diffusion and convection problems, pressure correction algorithims
	\item Overview of commercial CFD packages and their applications. Benefits and limitations, errors and accuracy
\end{itemize}
\subsection{Assignment}
2 CFD assignment files. Intake Manifold Study (PDF) to be the one most relevant.

These files pertain to the description of the assignment you must complete. The assignment is split in two parts, which however will make a whle paper.report.
\begin{itemize}
	\item The first part should include the \textit{Introduction} and the \textit{Numerical Methods} sections of the paper/report.
	\item The second part should include the \textit{Results, Discussion and Conclusions} sections of the paper/report
\end{itemize}
To be submitted as a PDF document with a set format. 